### 2012-11-14 counterexample to bratman on shared intention/a counterexample to bratman on shared intention.tex
very rough
first draft done, proof read (sort of)

\def \ititle {A Counterexample to Bratman on Shared Intention}
\def \isubtitle {}
\def \iauthor {Stephen A.\ Butterfill}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

@@

\begin{abstract}
\noindent
At the centre of one leading account of shared agency, Michael Bratman's, is the claim that certain conditions are sufficient for us to have a shared intention that we J.
This paper provides a counterexample to the sufficiency of these conditions and suggests a way of strengthening them to avoid the counterexample.
%The counterexample exploits the possibility of two agents meeting Bratman's conditions for shared intention even though each conceives of the other's intentions and actions only as constraints to work around and opportunities to avoid.
%Shared intention requires more than this: and it may require that the agents conceive of all of their actions as parts of a single plan.
\end{abstract}

\section{Shared Intention}
Why, if at all, is a notion of shared intention needed? 
This question is standardly answered by appeal to contrast cases \citep[compare][p.\ 150]{Bratman:2009lv}.
Thus \citet{gilbert_walking_1990} contrasts friends intentionally walking together with two people who happen to be walking side by side. 
And \citet{Searle:1990em} contrasts park visitors who  simultaneously run to a central shelter in performing a dance with park visitors who likewise run to the central shelter but only because of an impending storm.
%And Bratman (\citeyear{Bratman:1992mi}, p.\ 333; \citeyear{Bratman:1993je}, p.\ 103--4) contrasts two people who cooperatively plan to go to New York  together with two people who each have an intention that they go to New York together by way of coercing the other into travelling with her.
These and other contrast cases invite the question, 
How do cases involving shared agency differ from cases involving parallel agency only?

@@

`3. 1 and 2 are common knowledge between us' \citep[][p.\ View 4]{Bratman:1993je}
\end{quote}
%
In this paper we give a counterexample to Bratman's  claim that the above conditions, (1)--(3), are collectively sufficient conditions for shared intention. 
We shall also suggest a revision to avoid the counterexample.
%Apart from improving our understanding of what shared intention is, this will also bear on the kinds of planning that are involved in acting together.

Before going further we must distinguish two versions of the claim that (1)--(3) are collectively sufficient for shared intention.
The \emph{weak claim} is that there is some J such that these conditions are sufficient for you and I to intend that we J.
The \emph{strong claim} is that for any J, these conditions are sufficient for you and I to intend that we J.
One of Bratman's aims is to show that an account of shared intention can be \emph{conceptually conservative}:
he aims, that is, to show that it is possible to give an account of shared intention using concepts that `are available within the theory of individual planning agency' \citep[p.\ 163]{Bratman:2009lv}.  
Achieving this aim would require the strong claim, and it is to the strong claim that our counterexample is directed.

How could we show that our meeting Bratman's conditions, (1)--(3), is not in fact sufficient for us to have a shared intention? 
We seek a case where the conditions are met although we lack a shared intention.
But how could we determine that we lack a shared intention?
As already mentioned, the notion of shared intention is supposed to 
	make it possible to 
	characterise systematically a difference between 
		cases involving shared agency (such as our walking together)
		and
		cases involving parallel agency only (such as two strangers who happen to be walking the same route side-by-side). 
Suppose, then, that we had a trio of cases, A, B and C, each involving two agents.
Suppose, further, that A and B involved parallel agency only, whereas C involved shared agency.
Then we could be sure that A and B do not involve shared intention.
Now suppose 
	that, for some relevant J, Bratman's conditions, (1)--(3) above, were met in cases B and C alike, 
	that in each case the structure of intention and knowledge played an appropriate role in guiding the agents' actions,
	and that in each case the agents thereby successfully J.
Then case B would be our counterexample:
Bratman's conditions are met but there is no shared intention.
This is how our counterexample will work.

@@

A consequence is that, in the right situations, one of us can rationally intend that we J, and can intend this unilaterally, that is without depending on anyone else intending that we J. 
Suppose you know that I am going to Chicago via a certain route at a particular time, 
and that I will do this regardless of what you do.
Suppose also that you can rationally intend that you go to Chicago in the same manner,
and that you know that if you act on this intention the upshot will be that we will go to Chicago together (although I may not know that we are going together---perhaps you will conceal your presence from me).
Then you can rationally intend that we go to Chicago together, 
	and you can intend this irrespective of whether I have any corresponding intention---providing, of course, that in so intending you are conceiving of our going to Chicago together in a way that is neutral with respect to shared intentionality.
What follows depends on the premise that this is indeed possible.%
\footnote{ 
\citet{Bratman:1999fr}  defends this claim at length. 
Note also that this claim must be true if Bratman's account of shared intention is to provide an informative and systematic distinction between the contrast cases mentioned at the start.
}

\section{Unshared Intentions}
As a further preliminary we need to introduce a definition.
Let us stipulate that we have an \emph{unshared intention} that we <J$_1$, J$_2$> where J$_1$$\neq$J$_2$ just if:
%
\begin{quote}
\label{df:unshared_intention}
1. (a) I intend that we J$_1$ and (b) you intend that we J$_2$

2. I intend that we J$_1$ in accordance with and because of la, lb, and meshing subplans of la and lb; you intend that we J$_2$ in accordance with and because of la, lb, and meshing subplans of la and lb

3. 1 and 2 are common knowledge between us.
\end{quote}
In defining unshared intention we have used conditions exactly like Bratman's sufficient conditions for shared intention except that Bratman's conditions have J$_1$$=$J$_2$.
At this point it might be natural for readers to suppose that agents could not have unshared intentions,
or at least that they could not do so without irrationality.
In this section we describe a possible situation in which two agents  have an unshared intention without irrationality, deception or even ignorance.
This possible situation is not the promised counterexample, but it does form the basis for it.

Let us first introduce the activity we shall focus on.
Ayesha and Benji  are playing a simple video game which involves moving a cross around a two-dimensional space littered with barriers.
Ayesha can only accelerate the cross backwards or forwards,
while Benji can only accelerate it left or right. 
The cross moves around and interacts with the barriers in ways both players can predict.
The players are given tasks independently. 
These tasks always involve making the cross hit a target within two minutes of starting. 
A player succeeds when the cross hits her target, regardless of what happens to the cross afterwards.  
(It may go on to hit another target.)
In this case, 
	Ayesha's task is to make the cross hit the red square
	while
	Benji's task is make the cross hit the blue circle. 
In general it is possible that either or both will succeed, or that they will both fail.
Each movement carries a small cost to the player who moves, so that Ayesha and Benji each attempt to minimize how much he or she moves the cross consistently with completing his or her task.
At the outset, 
Ayesha and Benji are each neutral on whether the other succeeds or fails.
They are not opponents and do not seek to undermine each other's efforts, but each is entirely concerned  with his or her own task.
All of this is common knowledge for Ayesha and Benji.
They both know who has which task, what constraints they face and what their motives are.

Consider the possibility of one player intending, unilaterally, that the two players do something.
Suppose that one of the players---Ayesha, say---can knowledgeably predict that if she performs a certain sequence actions, <a$_1$, a$_2$, ...\ a$_n$>, then Benji will simultaneously perform certain other actions, <b$_1$, b$_2$, ...\ b$_n$>,
 and the upshot will be that the cross hits the red square.
Were this to happen, it would be true that Ayesha and Benji made the cross hit the red square.
Suppose, further, that Ayesha can intend to perform those actions <a$_1$, a$_2$, ...\ a$_n$>.
Then Ayesha can intend, unilaterally, that they, Ayesha and Benji, make the cross hit the red square.

Unshared intentions require a kind of symmetry.
Let us suppose that the above sequences of actions,
	Ayesha's <a$_1$, a$_2$, ...\ a$_n$>  and 
	Benji's <b$_1$, b$_2$, ...\ b$_n$>,
will also result in the cross hitting the blue circle. 
(Since the cross has momentum, we can suppose that it will hit both the red square and the blue circle at some time after these action sequences have been performed.)
Then by the reasoning just offered, Benji could intend that they, Ayesha and Benji make the cross hit the blue circle.
So Ayesha and Benji could meet the first condition, (1), for having an unshared intention.

What about the second condition, (2)?
Suppose that Ayesha knows two further things.
First, that Benji intends that they, Ayesha and Benji, make the cross hit the blue circle.
Second, that in acting on his intention Benji will perform actions <b$_1$, b$_2$, ...\ b$_n$>.
Then Ayesha can intend that they, Ayesha and Benji, make the cross hit the red square in accordance with and because of her intention that they make the cross hit the red square and in accordance with and because of Benji's intention that they make the cross hit the blue circle.

This is not quite enough to meet the second condition, (2), because there is also a requirement about meshing subplans. 
To make apply this requirement we need to generalise Bratman's definition of meshing:
\begin{quote}
`our individual subplans concerning our J-ing \emph{mesh} just in case there is some way we could J that would not violate either of our subplans but would, rather, involve the successful execution of those subplans' \citep[p.\ 106]{Bratman:1993je}.
\end{quote}
A natural generalisation is this:
\begin{quote}
our individual subplans concerning our <J$_1$, J$_2$>-ing \emph{mesh} just in case there is some way I could J$_1$ and you could J$_2$ that would not violate either of our subplans but would, rather, involve the successful execution of those subplans. 
\end{quote}
%
To illustrate, 
there would be a failure to mesh if, in intending that they make the cross hit the red square,  Ayesha's plans had included pushing Benji out of the way and seizing his controls. 
There would also be a failure of mesh if Ayesha were planning to trick Benji into a situation where we would be unable to perform the actions he had been planning.
But in the case we have been describing there are no such failures to mesh.
Each agent's subplans involve manipulating his or her own controls,
and the successes each seeks in doing this depends on the other successfully carrying out their subplans.
So Ayesha can rationally intend that they, Ayesha and Benji, make the cross hit the red square in accordance with and because of their intentions and meshing subplans of them.
And Benji likewise for making the cross hit the blue circle.

The only outstanding requirement for Ayesha and Benji to have an unshared intention is that their various intentions are common knowledge. 
Assuming common knowledge is possible where agents have a shared intention, it is likewise possible in this case of unshared intention.
So Ayesha and Benji can have an unshared intention that they <J$_1$, J$_2$> where J$_1$ is Ayesha and Benji's making the cross hit the red square and J$_2$ is their making the cross hit the blue circle.

@@

%\section{Pure Unshared Intentions}
%We stipulate that an unshared intention is \emph{pure} if having that unshared intention does not involve having any shared intention. 
%It may be tempting to assume that all unshared intentions are pure. 
%This is not obvious, however, and may not even be true.
%Since Bratman provides only sufficient conditions for shared intention, his account doesn't tell us that an unshared intention is not a shared intention.
%For all Bratman says, the conditions defining unshared intention might also be collectively sufficient conditions for shared intention. 
%
%But doesn't shared agency require that there be a single activity, J-ing, about which each the agent involved has an intention? 
%This, too, is not obvious.  It might reasonably be denied by those who, like Bratman, reject the Simple View according to which when an individual intentionally J-s she has an intention concerning her J-ing \citep{Bratman:1984jr}.
%So the purity of an unshared intention cannot be assumed without argument. 
%This is why we do not rely on this assumption in what follows.
%
%%
%How can we show that Ayesha and Benji's unshared intention that they <J$_1$, J$_2$>  is pure?
%Perhaps we can appeal to intuition.
%Ayesha sees Benji's actions as constraints on her own, or else as opportunities.
%She exploits Benji's intentions for her own ends.
%Of course the situation is reciprocal: Benji exploits Ayesha in equal measure.
%Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
%and this is the full extent of their cooperation. 
%Perhaps it is clear enough that 
%the sort of shared agency that an account of shared intention is supposed to capture must involve more than this sort of reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.%
%\footnote{
%Note that we are not suggesting that reciprocal exploitation is incompatible with shared agency.  
%The claim under consideration here is rather that shared agency requires more than reciprocal exploitation.
%} 
%If so, we can already claim that Ayesha and Benji have a pure unshared intention.
%
%
%
%
%
%We started this paper by explaining the need for a notion of shared intention by appeal to contrast cases (following Bratman). 
%It is contrast cases that are supposed give us a pre-theoretical handle on shared intention.
%So to show that Ayesha and Benji's unshared intention is pure, we need to construct a contrasting case.
%
%***Lily and Isabel, 
%	like many people, 
% 	sometimes attribute intentions and other states to imaginary agents, and perform actions on their behalf. 
%In some cases this enables them to further their own real-world objectives (as in `Teddy wants to go to the park now').	
%Some of these imaginary agents are toys. 
%But some are imaginary aggregate agents. 
%Sometimes, that is, Lily and Isabel imagine that there is an agent distinct from either of them and such that all its parts are parts of them.
%They attribute intentions and other states to this agent, and act on its behalf.
%
%
%

@@

In the situation just described,
Ayesha and Benji are playing a game and have different tasks.
Thanks to special features of the game environment, they both succeed by acting on an unshared intention.
Now compare two further players, Yasmin and Zak, who are playing the same game. 
Their situations, knowledge states, intentions and actions are as similar as possible to Ayesha's and Benji's except for one detail.
Just by chance they have been assigned identical tasks: Yasmin's task is to make the cross hit the red square and Zak's task is the same.
So where Ayesha and Benji have an unshared intention that they <J$_1$, J$_2$>,
Yasmin and Zak meet Bratman's conditions (1)--(3) for having a shared intention that they J$_1$.  
But Yasmin, in planning and acting, does not rely on the coincidence of their intentions; and nor does Zak.
(Yasmin relies on the fact Zak intends that they J$_1$, of course; but she does not rely on the fact that Zak intends what she intends.)
Furthermore, due to an artefact of the way the game is structured,
the unshared intention and the Bratman intention (as we might label the structure of intention and knowledge while leaving open whether it constitutes a shared intention), result in the two pairs performing same actions in the same way.
That is, Yasmin reasons about Zak much as Ayesha reasons about Benji and Yasmin and does what Ayesha does, and likewise for Zak and Benji.

We claim that Yasmin and Zak have a shared intention that they J$_1$
only if 
Ayesha and Benji have a shared intention.%
\footnote{
Strictly speaking, 
	what matters for our argument is whether or not Ayesha and Benji have a shared intention \emph{in virtue of having the unshared intention that they <J$_1$, J$_2$>}.
	This is because, strictly speaking, we need to show, not that Yasmin and Zak lack any shared intention whatsoever, but only that they lack a shared intention that they J$_1$ in virtue of meeting Bratman's conditions. 
	For ease of exposition this is not made explicit in the main text.
} 
This claim follows from the similarities of the two cases.
The only difference is that Yasmin and Zak happen to be assigned the same task, whereas Ayesha and Benji are not.
And neither Yasmin nor Zak makes use of the fact that they have the same task. 
(This is not due to ignorance: it's just how they choose to approach their tasks.)
So if we consider on how  
		the case of Yasmin and Zak
	differs from
		 that of Ayesha and Benji,
we can see that these differences do not plausibly amount to a difference with respect to shared agency.
Shared intention cannot feature in one case but not the other.

To show that the case of Yasmin and Zak do not have a shared intention it remains only for us to show that Ayesha and Benji do not have one. 
Here we must be careful.
First note that,
	 since Bratman provides only sufficient conditions for shared intention, 
	 his account doesn't tell us that an unshared intention is not a shared intention.
For all Bratman says, the conditions defining unshared intention might  be sufficient for shared intention.

But doesn't shared intention require at least this much,
that there be a single activity  about which each the agent involved has an intention? 
This might reasonably be doubted by those who, like Bratman, reject the Simple View according to which when an individual intentionally F-s she has an intention concerning her F-ing \citep{Bratman:1984jr}.
So 
	we shall not infer  that Ayesha and Zak lack a shared intention
	just because (by construction) there is no F such that Ayesha and Zak's each intend that they, Ayesha and Zak, F.

Can we then appeal directly to intuition to show that Ayesha and Zak lack a shared intention?
Ayesha sees Benji's actions as constraints on her own, or else as opportunities.
She exploits Benji's intentions for her own ends.
Of course the situation is reciprocal: Benji exploits Ayesha in equal measure.
Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
and this is the full extent of their cooperation. 
We don't suppose that reciprocal exploitation is incompatible with shared intention. 
But Ayesha and Zak's interaction consists entirely in this sort reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.
Perhaps it is clear enough that 
the sort of shared agency that an account of shared intention is supposed to capture must involve more than this. 
If so, we can already claim that Ayesha and Benji are not acting on a shared intention.
But philosophers' intuitions about shared agency may not be entirely, so it would be better if we could avoid such a blunt appeal to intuition.

How else could we support the claim that Yasmin and Zak lack a shared intention? 
As mentioned at the start, 
the contrast cases are often used to anchor intuitions in theorising about shared agency.
In the next section we shall further support our claim by contrasting Yasmin and Zak's case with a further case, one which is as similar as possible and which does seem to involve shared agency.
The fact that Yasmin and Zak's case contrasts with this new case will support the claim that Yasmin and Zak lack shared intention.
This is the aim of the following section.
A first motive for introducing this new contrast case is that it provides an indication concerning what is missing from Bratman's account, and so may help us to understand why his conditions are not sufficient for shared intention.

>>>>

\def \ititle {Shared Agency Involves Changing Perspective: A Counterexample to Bratman}
\def \isubtitle {}
\def \iauthor {Stephen A.\ Butterfill}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

@@

\begin{abstract}
\noindent
The leading, best developed account of shared agency, Michael Bratman's, hinges on the claim that, roughly,
we have a shared intention if we each intend that we J and also that we J by way of these intentions and meshing subplans of them where this is all common knowledge.
This paper provides a counterexample to the sufficiency of this condition for shared intention.
The counterexample arises because it is possible for agents to meet the condition, and to act rationally on the specified knowledge and intentions,
 while conceiving of each other's actions only as constraints to work around and opportunities to exploit.
Shared agency requires more than this, or so we argue.
We also suggest a way of revising Bratman's account  that is consistent with his general approach.
In some or all cases, shared agency differs from individual agency in part because shared agency involves changing perspective so that one’s own and other’s actions are conceived of as parts of a single plan.

\end{abstract}

\section{Shared Intention}
Why, if at all, is a notion of shared intention needed? 
This question is standardly answered by appeal to contrast cases \citep[compare][p.\ 150]{Bratman:2009lv}.
Thus \citet{gilbert_walking_1990} contrasts friends intentionally walking together with two people who happen to be walking side by side. 
And \citet{Searle:1990em} contrasts park visitors who  simultaneously run to a central shelter in performing a dance with park visitors who likewise run to the central shelter but only because of an impending storm.
%And Bratman (\citeyear{Bratman:1992mi}, p.\ 333; \citeyear{Bratman:1993je}, p.\ 103--4) contrasts two people who cooperatively plan to go to New York  together with two people who each have an intention that they go to New York together by way of coercing the other into travelling with her.
These and other contrast cases invite the question, 
How do cases involving shared agency differ from cases involving only  parallel individual agency?

@@

`3. 1 and 2 are common knowledge between us' \citep[][p.\ View 4]{Bratman:1993je}.
\end{quote}
%
In this paper we give a counterexample to Bratman's  claim that the above conditions, (1)--(3), are collectively sufficient conditions for shared intention. 
We shall also suggest a revision to avoid the counterexample.
%Apart from improving our understanding of what shared intention is, this will also bear on the kinds of planning that are involved in acting together.

Before going further we must distinguish two versions of the claim that (1)--(3) are collectively sufficient for shared intention.
The \emph{weak claim} is that there is some J such that these conditions are sufficient for you and I to intend that we J.
The \emph{strong claim} is that for any J, these conditions are sufficient for you and I to intend that we J. 
Our initial counterexample will be directed to the strong claim.
However, after we have constructed this counterexample it will become clear that there are also counterexamples involving a wide range mundane activities to which Bratman explicitly takes his account to apply.
Even walking together%
	\footnote{
	See \citet[p.\ 150]{Bratman:2009lv}.
	}
	%
and painting a house together%
	\footnote{
	See \citet[p.\ 331]{Bratman:1992mi}.
	}
	%
can serve as counterexamples.
%One of Bratman's aims is to show that an account of shared intention should be \emph{conceptually conservative}.
%He aims, that is, to show that  it is possible to give an account of shared intention using only concepts that `are available within the theory of individual planning agency' \citep[p.\ 163]{Bratman:2009lv}.  
%Achieving this aim would require the strong claim, and it is to the strong claim that our counterexample is directed.%
%\footnote{
%We do not aim to attack the claim that it is possible to give a conceptually conservative account of shared intention. 
%The point we are making here is just that if an account
%}

How could we show that our meeting Bratman's conditions, (1)--(3), is not in fact sufficient for us to have a shared intention? 
We seek a case where the conditions are met although we lack a shared intention.
But how could we determine that we lack a shared intention?
As already mentioned, the notion of shared intention is supposed to 
	make it possible to 
	characterise systematically a difference between 
		cases involving shared agency (such as our walking together)
		and
		cases involving only parallel  individual agency (such as two strangers who happen to be walking the same route side-by-side). 
Suppose, then, that we had a trio of cases, A, B and C, each involving two agents.
Suppose, further, that A and B involved parallel agency only, whereas C involved shared agency.
Then we could be sure that A and B do not involve shared intention.
Now suppose 
	that, for some relevant J, Bratman's conditions, (1)--(3) above, were met in cases B and C alike, 
	that in each case the structure of intention and knowledge played an appropriate role in guiding the agents' actions,
	and that in each case the agents thereby successfully J.
Then case B would be our counterexample:
Bratman's conditions are met but there is no shared intention.
This is how our counterexample will work.
(Strictly speaking, case A is not necessary; but including it simplifies exposition.)

@@

To illustrate, first consider Bratman's `mafia case' where two people go to New York together by virtue of one of them forcing the other into a car and driving off \citep[p.\ 333]{Bratman:1992mi}. 
Next consider a paradigm case of where two friends cooperatively go to New York together.
It's possible to conceive of an act type of going to New York together which is broad enough that both cases, the coercive and the cooperative, fall under it.
And it's even possible to desire or intend to be involved in an act of this type.
A gangster might intend to go to New York with a future victim without having yet decided whether they will do this cooperatively or coercively.

A consequence is that, in the right situations, one of us can rationally intend that we J, and can intend this unilaterally, that is without depending on anyone else intending that we J. 
Suppose you know that I am going to New York via a certain route at a particular time, 
and that I will do this regardless of what you do.
Suppose also that you can rationally intend that you go to New York in the same manner,
and that you know that if you act on this intention the upshot will be that we will go to New York together (although I may not know that we are going together---perhaps you will conceal your presence from me).
Then you can rationally intend that we go to New York together, 
	and you can intend this irrespective of whether I have any corresponding intention---providing, of course, that in so intending you are conceiving of our going to New York together in a way that is neutral with respect to shared intentionality.
What follows depends on the premise that this is indeed possible.%
\footnote{ 
\citet{Bratman:1999fr}  defends this claim at length. 
Note also that this claim must be true if Bratman's account of shared intention is to provide an informative and systematic distinction between the contrast cases mentioned at the start.
}

\section{Unshared Intentions}
As a further preliminary we need to introduce a definition.
Let us stipulate that we have an \emph{unshared intention} that we <J$_1$, J$_2$> where J$_1$$\neq$J$_2$ just if:
%
\begin{quote}
\label{df:unshared_intention}
1$^\prime$. (a) I intend that we J$_1$ and (b) you intend that we J$_2$

2$^\prime$. I intend that we J$_1$ in accordance with and because of la, lb, and meshing subplans of la and lb; you intend that we J$_2$ in accordance with and because of la, lb, and meshing subplans of la and lb

3$^\prime$. 1 and 2 are common knowledge between us.
\end{quote}
In defining unshared intention we have used conditions exactly like Bratman's sufficient conditions for shared intention except that Bratman's conditions have J$_1$$=$J$_2$.
At this point it might be natural for readers to suppose that agents could not have unshared intentions,
or at least that they could not do so without irrationality.
In this section we describe a possible situation in which two agents  have an unshared intention without irrationality, deception or even ignorance.
This possible situation is not the promised counterexample, but it does form the basis for it.

Let us first introduce the activity we shall focus on.
Ayesha and Ahmed  are playing a simple video game which involves moving a cross around a two-dimensional space littered with barriers.
Ayesha can only accelerate the cross backwards or forwards,
while Ahmed can only accelerate it left or right. 
The cross moves around and interacts with the barriers in ways both players can predict.
The players are given tasks independently. 
These tasks always involve making the cross hit a target within two minutes of starting. 
A player succeeds when the cross hits her target, regardless of what happens to the cross afterwards.  
(It may go on to hit another target.)
In this case, 
	Ayesha's task is to make the cross hit the red square
	while
	Ahmed's task is make the cross hit the blue circle. 
In general it is possible that either or both will succeed, or that they will both fail.
Each movement carries a small cost to the player who moves, so that Ayesha and Ahmed each attempt to minimize how much he or she moves the cross consistently with completing his or her task.
At the outset, 
Ayesha and Ahmed are each neutral on whether the other succeeds or fails.
They are not opponents and do not seek to undermine each other's efforts, but each is entirely concerned  with his or her own task.
All of this is common knowledge for Ayesha and Ahmed.
They both know who has which task, what constraints they face and what their motives are.

Consider the possibility of one player intending, unilaterally, that the two players do something.
Suppose that one of the players---Ayesha, say---can knowledgeably predict that if she performs a certain sequence actions, <a$_1$, a$_2$, ...\ a$_n$>, then Ahmed will simultaneously perform certain other actions, <b$_1$, b$_2$, ...\ b$_n$>,
 and the upshot will be that the cross hits the red square.
Were this to happen, it would be true that Ayesha and Ahmed made the cross hit the red square.
Suppose, further, that Ayesha can intend to perform those actions <a$_1$, a$_2$, ...\ a$_n$>.
Then Ayesha can intend, unilaterally, that they, Ayesha and Ahmed, make the cross hit the red square (see Section \vref{sec:netural_wrt_shared_intentionality}).

Unshared intentions require a kind of symmetry.
Let us suppose that the above sequences of actions,
	Ayesha's <a$_1$, a$_2$, ...\ a$_n$>  and 
	Ahmed's <b$_1$, b$_2$, ...\ b$_n$>,
will also result in the cross hitting the blue circle. 
(Since the cross has momentum, we can suppose that it will hit both the red square and the blue circle at some time after these action sequences have been performed.)
Then by the reasoning just offered, Ahmed could intend that they, Ayesha and Ahmed make the cross hit the blue circle.
So Ayesha and Ahmed could meet the first condition, (1), for having an unshared intention.

What about the second condition, (2)?
Suppose that Ayesha knows two further things.
First, that Ahmed intends that they, Ayesha and Ahmed, make the cross hit the blue circle.
Second, that in acting on his intention Ahmed will perform actions <b$_1$, b$_2$, ...\ b$_n$>.
Then Ayesha can intend that they, Ayesha and Ahmed, make the cross hit the red square in accordance with and because of her intention that they make the cross hit the red square and in accordance with and because of Ahmed's intention that they make the cross hit the blue circle.

This is not quite enough to meet the second condition, (2), because there is also a requirement about meshing subplans. 
To apply this requirement we need to generalise Bratman's definition of meshing:
\begin{quote}
`our individual subplans concerning our J-ing \emph{mesh} just in case there is some way we could J that would not violate either of our subplans but would, rather, involve the successful execution of those subplans' \citep[p.\ 106]{Bratman:1993je}.
\end{quote}
A natural generalisation is this:
\begin{quote}
our individual subplans concerning our <J$_1$, J$_2$>-ing \emph{mesh} just in case there is some way I could J$_1$ and you could J$_2$ that would not violate either of our subplans but would, rather, involve the successful execution of those subplans. 
\end{quote}
%
To illustrate, 
their subplans would fail to mesh if, in intending that they make the cross hit the red square,  Ayesha's plans had included pushing Ahmed out of the way and seizing his controls. 
They would also fail to mesh if Ayesha were planning to trick Ahmed into a situation where we would be unable to perform the actions he had been planning.
But in the case we have been describing, the agents subplans mesh perfectly.
Each agent's subplans involve manipulating his or her own controls,
and the successes each seeks in doing this depends on the other successfully carrying out their subplans.
So Ayesha can rationally intend that they, Ayesha and Ahmed, make the cross hit the red square in accordance with and because of their intentions and meshing subplans of them.
And Ahmed likewise for making the cross hit the blue circle.

The only outstanding requirement for Ayesha and Ahmed to have an unshared intention is that their various intentions are common knowledge. 
Assuming common knowledge is possible concerning Bratman's conditions (1)--(2) on page \pageref{quote:bratman_account}, 
it is likewise possible for the corresponding conditions on unshared intention, (1$^\prime$)--(2$^\prime$) on page  \pageref{df:unshared_intention}.
So Ayesha and Ahmed can have an unshared intention that they <J$_1$, J$_2$> where J$_1$ is Ayesha and Ahmed's making the cross hit the red square and J$_2$ is their making the cross hit the blue circle.

@@

%\section{Pure Unshared Intentions}
%We stipulate that an unshared intention is \emph{pure} if having that unshared intention does not involve having any shared intention. 
%It may be tempting to assume that all unshared intentions are pure. 
%This is not obvious, however, and may not even be true.
%Since Bratman provides only sufficient conditions for shared intention, his account doesn't tell us that an unshared intention is not a shared intention.
%For all Bratman says, the conditions defining unshared intention might also be collectively sufficient conditions for shared intention. 
%
%But doesn't shared agency require that there be a single activity, J-ing, about which each the agent involved has an intention? 
%This, too, is not obvious.  It might reasonably be denied by those who, like Bratman, reject the Simple View according to which when an individual intentionally J-s she has an intention concerning her J-ing \citep{Bratman:1984jr}.
%So the purity of an unshared intention cannot be assumed without argument. 
%This is why we do not rely on this assumption in what follows.
%
%%
%How can we show that Ayesha and Ahmed's unshared intention that they <J$_1$, J$_2$>  is pure?
%Perhaps we can appeal to intuition.
%Ayesha sees Ahmed's actions as constraints on her own, or else as opportunities.
%She exploits Ahmed's intentions for her own ends.
%Of course the situation is reciprocal: Ahmed exploits Ayesha in equal measure.
%Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
%and this is the full extent of their cooperation. 
%Perhaps it is clear enough that 
%the sort of shared agency that an account of shared intention is supposed to capture must involve more than this sort of reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.%
%\footnote{
%Note that we are not suggesting that reciprocal exploitation is incompatible with shared agency.  
%The claim under consideration here is rather that shared agency requires more than reciprocal exploitation.
%} 
%If so, we can already claim that Ayesha and Ahmed have a pure unshared intention.
%
%
%
%
%
%We started this paper by explaining the need for a notion of shared intention by appeal to contrast cases (following Bratman). 
%It is contrast cases that are supposed give us a pre-theoretical handle on shared intention.
%So to show that Ayesha and Ahmed's unshared intention is pure, we need to construct a contrasting case.
%
%***Caitlin and Ciaran, 
%	like many people, 
% 	sometimes attribute intentions and other states to imaginary agents, and perform actions on their behalf. 
%In some cases this enables them to further their own real-world objectives (as in `Teddy wants to go to the park now').	
%Some of these imaginary agents are toys. 
%But some are imaginary aggregate agents. 
%Sometimes, that is, Caitlin and Ciaran imagine that there is an agent distinct from either of them and such that all its parts are parts of them.
%They attribute intentions and other states to this agent, and act on its behalf.
%
%
%

@@

In the situation just described,
Ayesha and Ahmed are playing a game and have different tasks.
Thanks to special features of the game environment, they both succeed by acting on an unshared intention.
Now compare two further players, Beatrice and Baldric, who are playing the same game. 
Their situations, knowledge states, intentions and actions are as similar as possible to Ayesha's and Ahmed's except for one detail.
Just by chance they have been assigned identical tasks: Beatrice's task is to make the cross hit the red square and Baldric's task is the same.
So where Ayesha and Ahmed have an unshared intention that they <J$_1$, J$_2$>,
Beatrice and Baldric meet Bratman's conditions (1)--(3) for having a shared intention that they J$_1$.  
But Beatrice, in planning and acting, does not rely on the coincidence of their intentions; and nor does Baldric.
(Beatrice relies on the fact Baldric intends that they J$_1$, of course; but she does not rely on the fact that Baldric intends what she intends.)
Furthermore, due to an artefact of the way the game is structured,
the unshared intention and the 
	Bratman intention 
	\label{df:bratman_intention}
	(as we might label the structure of intention and knowledge while leaving open whether it constitutes a shared intention), result in the two pairs performing same actions in the same way.
That is, Beatrice reasons about Baldric much as Ayesha reasons about Ahmed and Beatrice and does what Ayesha does, and likewise for Baldric and Ahmed.

We claim that Beatrice and Baldric have a shared intention that they J$_1$
only if 
Ayesha and Ahmed have a shared intention.%
\footnote{
Strictly speaking, 
	what matters for our argument is whether Ayesha and Ahmed have a shared intention \emph{in virtue of having the unshared intention that they <J$_1$, J$_2$>}.
	This is because, strictly speaking, we need to show, not that Beatrice and Baldric lack any shared intention whatsoever, but only that they lack a shared intention that they J$_1$ just in virtue of meeting Bratman's conditions (see (1)--(3) on page  \pageref{quote:bratman_account}). 
	For ease of exposition this is not made explicit in the main text.
} 
This claim follows from the similarities of the two cases.
The only difference is that Beatrice and Baldric happen to be assigned the same task, whereas Ayesha and Ahmed are not.
And neither Beatrice nor Baldric makes use of the fact that they have the same task. 
(This is not due to ignorance: it's just how they choose to approach their tasks.)
So if we consider on how  
		the case of Beatrice and Baldric
	differs from
		 that of Ayesha and Ahmed,
we can see that these differences do not plausibly amount to a difference with respect to shared agency.
Shared intention cannot feature in one case but not the other.

To show that Beatrice and Baldric do not have a shared intention it remains only for us to show that Ayesha and Ahmed do not have one. 
Here we must be careful.
First note that,
	 since Bratman provides only sufficient conditions for shared intention, 
	 his account doesn't tell us that an unshared intention is not a shared intention.
For all Bratman says, the conditions defining unshared intention might  be sufficient for shared intention.

But doesn't shared intention require at least this much,
that there be a single activity  about which each the agent involved has an intention? 
This might reasonably be doubted by those who, like Bratman, reject the Simple View according to which when an individual intentionally F-s she has an intention concerning her F-ing \citep{Bratman:1984jr}.
So 
	we shall not infer  that Ayesha and Ahmed lack a shared intention
	just because (by construction) there is no F such that Ayesha and Ahmed each intend that they, Ayesha and Ahmed, F.

Can we then appeal directly to intuition to show that Ayesha and Ahmed lack a shared intention?
Ayesha sees Ahmed's actions as constraints on her own, or else as opportunities.
She exploits Ahmed's intentions for her own ends.
Of course the situation is reciprocal: Ahmed exploits Ayesha in equal measure.
Each allows himself or herself to be exploited by the other because being exploited enables exploiting,
and this is the full extent of their cooperation. 
We don't suppose that reciprocal exploitation is incompatible with shared intention. 
But Ayesha and Ahmed's interaction consists entirely in this sort reciprocal exploitation, where each agent sees the other's actions only as constraints or opportunities.
Perhaps it is clear enough that 
the sort of shared agency that an account of shared intention is supposed to capture must involve more than this. 
If so, we can already claim that Ayesha and Ahmed are not acting on a shared intention.
But philosophers' intuitions about shared agency may not be entirely, so it would be better if we could avoid such a blunt appeal to intuition.
